---
title: "Visualizing Pupillometry Data"
description: |
  A demonstration on how to plot uncertainty (i.e., standard errors) using pupillometry data.
author:
  - name: Ashley L. Miller 
    url: 
    affiliation: University of Oregon
    affiliation_url: https://psychology.uoregon.edu/
date: 03-13-2019
output:
  distill::distill_article:
    self_contained: false
categories:
  - dataviz
  - pupillometry
  - EDLD final project
---

```{r setup, include=FALSE}

# Set knitr options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 7.5,
                      fig.height = 4.5)

# Load packages
#devtools::install_github("datalorax/sundry")
#devtools::install_github("wilkelab/ungeviz")
#install.packages("pkgconfig")
#install.packages("rio")
#install.packages("here")
#install.packages("tidyverse")
#install.packages("magrittr")
#install.packages("ggforce")
#install.packages("rcartocolor")
#install.packages("showtext")
#install.packages("gganimate")
#install.packages("glue")
#install.packages("mgcv")
#install.packages("transformr")
#install.packages("RColorBrewer")
#install.packages("knitr")
#install.packages("jpeg")
#install.packages("gifski")
#install.packages("colorspance)

library(pkgconfig)
library(rio)
library(here)
library(tidyverse)
library(magrittr)
library(ggforce)
library(rcartocolor)
library(showtext)
library(sundry)
library(ungeviz)
library(gganimate)
library(glue)
library(mgcv)
#library(gifski)
library(transformr)
library(RColorBrewer)
library(knitr)
library(colorspace)
library(rmarkdown)

# Disable scientific notation
options(scipen = 999)

academic_theme <- theme(plot.subtitle = element_text(family = "Times"), 
                        plot.caption  = element_text(family = "Times", 
                                                     size = 12,
                                                     hjust = 0), 
                        axis.title    = element_text(family = "Times", 
                                                     face = "bold"), 
                        axis.text     = element_text(family = "Times"), 
                        axis.text.x   = element_text(family = "Times"), 
                        axis.text.y   = element_text(family = "Times"), 
                        plot.title    = element_text(family = "Times", 
                                                     face = "bold"), 
                        legend.text   = element_text(family = "Times"), 
                        legend.title  = element_text(family = "Times"), 
                        strip.text    = element_text(family = "Times"),
                        panel.grid.major = element_line(colour = "white"), 
                        panel.grid.minor = element_line(colour = "white"))

bbg_darktheme <- theme(panel.grid.major = element_line(colour = "gray10"), 
                       panel.grid.minor = element_line(colour = "gray10"), 
                       axis.text = element_text(colour = "gray80"), 
                       axis.text.x = element_text(colour = "gray80"), 
                       axis.text.y = element_text(colour = "gray80"),
                       axis.title = element_text(colour = "gray80", 
                                                 face = "bold"),
                       axis.ticks = element_line(colour = "gray80"),
                       axis.line = element_line(colour = "gray80"),
                       legend.text = element_text(colour = "gray80"), 
                       legend.title = element_text(colour = "gray80"), 
                       plot.subtitle = element_text(colour = "gray80"),
                       strip.text = element_text(colour = "gray80", 
                                                 face = "bold"),
                       panel.background = element_rect(fill = "gray10"),                     
                       plot.background = element_rect(fill = "gray10"), 
                       legend.background = element_rect(fill = NA, 
                                                        color = NA), 
                       plot.margin = margin(10, 10, b = 20, 10),
                       plot.caption = element_text(colour = "gray80", 
                                                   vjust = 1, 
                                                   hjust = 0,
                                                   size = 10.5), 
                       plot.title = element_text(colour = "gray80", 
                                                 face = "bold"))

```

Up until now, to visualize data in my own research, I would obtain means and standard errors in SPSS, then plot the data in Excel. This practice isn't exactly what I'd call ideal. So, the purpose of this post is to demonstrate various methods of visualizing uncertainty in `R`, with a particular emphasis on visualizing pupillometry data.

The data-set I will be using for this demonstration is de-identified and already hosted on Github. The data come from one of my recent publications (Experiment 1; [Miller, Gross, & Unsworth, 2019](https://www.sciencedirect.com/science/article/pii/S0749596X18300846)). In this paper, pupil dilation was used as an index of the intensity of attention to determine if variation in attention at encoding partially accounts for the relation between working memory capacity (WMC) and long-term memory performance (LTM). Participants (*N* = 138) completed a battery of complex span working memory tasks, followed by a delayed free recall task while pupil dilation was simultaneously recorded.

Before beginning, let's first load and inspect the data:

```{r load_data}
data <- import(here("data", "DeIntentifiedJML2019Data_Exp1.sav"),
               setclass = "tibble") %>% 
  characterize() %>%
  janitor::clean_names()

paged_table(data)
```

There are many variables in this data-set that I won't need for the purpose of this demonstration. Some of the variable names are also a bit confusing. So, I need to select the key variables of interest and rename the remaining variables:

```{r tidy_rename}
# Select variables of interest for pupil data
pupil_data <- data %>%
  select(-sp1_acc:-symspan, 
         -ineffective:-recency_recall,
         -baseline_pupil_mean:-tepr_recency)

# Cam's efficient method to rename bin/word variables
# E.g., data currently reads ebin1w1pt4_mean
# I just want the variable to read bin1w1
pupil_data %<>%
  rename_at(
    vars(starts_with("ebin")),
    funs(
      paste(
        str_extract(., "w\\d{1,2}"),
        "_",
        str_extract(., "bin\\d{1,2}"),
        sep = "")))

paged_table(pupil_data)
```

There, much better. 

## Plot 1

The first plot shows changes in pupil diameter across the 3 second study/encoding phase for each word (i.e., bin). As a starting point, see below (was Fig. 4 in [Miller et al. (2019)](https://www.sciencedirect.com/science/article/pii/S0749596X18300846):

The intended audience for this graph is the **scientific community**, but it is also my hope that interested laypersons may also be able to understand it. The message to be communicated is that when instructed to study a list of words for a later test, pupil diameter increases throughout the study phase for each word. This increase in pupil dilation is believed to reflect an increase in the amount of attentional effort devoted to a given item.

Data prep (some tidying will be required) and code for plot:

```{r tidy_plot1_showcodeonly, echo=TRUE, eval=FALSE}

# Tidy data:
pupil_data %<>%
  gather(key = word_bin, value = TEPR, w1_bin1:w10_bin15) %>%
  separate(word_bin, c("word", "bin"), sep = "_") %>%
  mutate(word = parse_number(word),
         bin = parse_number(bin)) %>%
  arrange(subject)

plot1_data <- pupil_data %>%
  group_by(bin) %>%
  summarise(mean_TEPR = mean(TEPR, na.rm = TRUE),
            se_TEPR = sundry::se(TEPR))

# This just makes the line begin at x = 0 and y = 0
plot1_data <- rbind(plot1_data, "1st" = c(0, 0, 0)) 

plot1_OG <- ggplot(plot1_data, aes(x = bin, y = mean_TEPR)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_TEPR - se_TEPR, 
                    ymax = mean_TEPR + se_TEPR),
                    color = "gray10",
                    width = 0.4, 
                    size = 0.6) +
  theme_bw(base_size = 12) +
  # Change labels
  labs(caption = "Figure 1. Task evoked pupillary response across the 3 second 
                  study (encoding) phase for each word",
       y = "Change in Pupil Diameter (mm)",
       x = "Time (ms)") +
  # Relabel x axis values to make more sense to reader
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 
                                  9, 10, 11, 12, 13, 14, 15),
                     labels = c("", "400", "", "800", "", 
                                "1,200", "", "1,600", "", "2,000", 
                                "", "2,400", "", "2,800", ""),
                     limits = c(1, NA))

```

```{r tidy_plot1DNU, include=FALSE, echo=FALSE, eval=TRUE}

# Tidy data:
pupil_data %<>%
  gather(key = word_bin, value = TEPR, w1_bin1:w10_bin15) %>%
  separate(word_bin, c("word", "bin"), sep = "_") %>%
  mutate(word = parse_number(word),
         bin = parse_number(bin)) %>%
  arrange(subject)

plot1_data <- pupil_data %>%
  group_by(bin) %>%
  summarise(mean_TEPR = mean(TEPR, na.rm = TRUE),
            se_TEPR = sundry::se(TEPR))

# This just makes the line begin at x = 0 and y = 0
plot1_data <- rbind(plot1_data, "1st" = c(0, 0, 0)) 

plot1_OG <- ggplot(plot1_data, aes(x = bin, y = mean_TEPR)) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_TEPR - se_TEPR, 
                    ymax = mean_TEPR + se_TEPR),
                    color = "gray10",
                    width = 0.4, 
                    size = 0.6) +
  theme_bw(base_size = 12) +
  # Change labels
  labs(caption = "Figure 1. Task evoked pupillary response across the 3 second study (encoding) phase for each word",
       y = "Change in Pupil Diameter (mm)",
       x = "Time (ms)") +
  # Relabel x axis values to make more sense to reader
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 
                                  9, 10, 11, 12, 13, 14, 15),
                     labels = c("", "400", "", "800", "", 
                                "1,200", "", "1,600", "", "2,000", 
                                "", "2,400", "", "2,800", ""),
                     limits = c(1, NA))
```

```{r tidy_data_plot1USE, fig.height=4.5, fig.width=7.5, fig.align='center'}
plot1_OG + academic_theme
```

### Alternative Publication-Friendly Version of Plot 1

While the above plot is perfectly fine for publication purposes, I intend to enhance this plot in a number of ways. But, namely, I want to map uncertainty (previously shown with the standard error bars) via bootstrapping/generation of outcome draws from a fitted model. For more details on this method, I highly recommend reading up on Claus O. Wilke's [ungeviz package](https://wilkelab.org/ungeviz/articles/posterior-draws.html). Another good reference can be located [here](https://wilkelab.org/ungeviz/reference/bootstrapper.html).

```{r plot1DNU, include=FALSE, echo=FALSE, eval=TRUE}

# I want to model uncertainty with bootstrapping:
row_samps <- rerun(100,
      sample(seq_len(nrow(plot1_data)), 
             nrow(plot1_data), 
             replace = TRUE))

# Extracting samples
d_samps <- map_df(row_samps, ~plot1_data[., ], .id = "sample")

# Plotting both data sources (my data and hypothetical/bootstrapped data)
plot1_academic <- ggplot(plot1_data, aes(x = bin, y = mean_TEPR)) +
    stat_smooth(aes(group = sample),
              data = d_samps,
              geom = "line",
              color = "gray60",
              fullrange = TRUE,
              size = 0.1) +
    geom_smooth(color = "black", se = FALSE, size = 0.9) +
    theme_bw(base_size = 12) +
    # Change labels
    labs(caption = "Figure 1. Task evoked pupillary response across the 3 second study (encoding) phase for each word",
           y = "Change in Pupil Diameter (mm)",
           x = "Time (ms)") +
    # Relabel x axis values to make more sense to reader
    scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 
                                  9, 10, 11, 12, 13, 14, 15),
                       labels = c("0", "", "400", "", "800", "", 
                                  "1,200", "", "1,600", "", "2,000", 
                                  "", "2,400", "", "2,800", ""),
                       limits = c(0, NA)) +
    # Add text specifying when stimuli appear onscreen
    geom_text(y = 0.04,
              x = 1.4,
              color = "black",
              label = "      To-be-remembered
              word appears onscreen", 
              size = 4, 
              fontface = 2, 
              family = "Times") +
    # Add dotted vertical line at x = 0
    geom_vline(aes(xintercept = 0),
               color = "gray50", 
               lty = "dashed")

```

```{r p1v2_showcodeonly, echo=TRUE, eval=FALSE}

# I want to model uncertainty with bootstrapping:
row_samps <- rerun(100,
      sample(seq_len(nrow(plot1_data)), 
             nrow(plot1_data), 
             replace = TRUE))

# Extracting samples
d_samps <- map_df(row_samps, ~plot1_data[., ], .id = "sample")

# Plotting both data sources (my data and hypothetical/bootstrapped data)
plot1_academic <- ggplot(plot1_data, aes(x = bin, y = mean_TEPR)) +
    stat_smooth(aes(group = sample),
              data = d_samps,
              geom = "line",
              color = "gray60",
              fullrange = TRUE,
              size = 0.1) +
    geom_smooth(color = "black", se = FALSE, size = 0.9) +
    theme_bw(base_size = 12) +
    # Change labels
    labs(caption = "Figure 1. Task evoked pupillary response across the 3 second 
                    study (encoding) phase for each word",
           y = "Change in Pupil Diameter (mm)",
           x = "Time (ms)") +
    # Relabel x axis values to make more sense to reader
    scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 
                                  9, 10, 11, 12, 13, 14, 15),
                       labels = c("0", "", "400", "", "800", "", 
                                  "1,200", "", "1,600", "", "2,000", 
                                  "", "2,400", "", "2,800", ""),
                       limits = c(0, NA)) +
    # Add text specifying when stimuli appear onscreen
    geom_text(y = 0.04,
              x = 1.4,
              color = "black",
              label = "      To-be-remembered
              word appears onscreen", 
              size = 4, 
              fontface = 2, 
              family = "Times") +
    # Add dotted vertical line at x = 0
    geom_vline(aes(xintercept = 0),
               color = "gray50", 
               lty = "dashed")

```

```{r academic_theme_print, fig.height=4.5, fig.width=7.5, fig.align='center'}
# Apply an academic theme to plot
plot1_academic + academic_theme
```

### Fancier/Prettier Version of Plot 1

Here I apply my own theme:

```{r plot1_custom_themeDNU, include=FALSE, echo=FALSE, eval=TRUE}
# Plotting both data sources (my data and hypothetical/bootstrapped data)
plot1_fun <- ggplot(plot1_data, aes(x = bin, y = mean_TEPR)) +
    stat_smooth(aes(group = sample),
              data = d_samps,
              geom = "line",
              color = "#2DDADA",
              fullrange = TRUE,
              size = 0.1) +
    geom_smooth(color = "magenta", se = FALSE, size = 0.9) +
    theme_minimal(base_size = 12) +
    # Change labels
    labs(caption = "Figure 1. Task evoked pupillary response across the 3 second study (encoding) phase for each word",
           y = "Change in Pupil Diameter (mm)",
           x = "Time (ms)") +
    # Relabel x axis values to make more sense to reader
    scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 
                                  9, 10, 11, 12, 13, 14, 15),
                       labels = c("0", "", "400", "", "800", "", 
                                  "1,200", "", "1,600", "", "2,000", 
                                  "", "2,400", "", "2,800", ""),
                       limits = c(0, NA)) +
    # Add text specifying when stimuli appear onscreen
    geom_text(y = 0.04,
              x = 1.6,
              color = "gray80",
              label = "      To-be-remembered
              word appears onscreen", size = 4, fontface = 2) +
    # Add dotted vertical line at x = 0
    geom_vline(aes(xintercept = 0),
               color = "gray80", 
               lty = "dashed")
```

```{r plot1_print_custom, fig.height=4.5, fig.width=7.5, fig.align='center'}
plot1_fun + bbg_darktheme
```

Pretty nice, eh? :)

## Plot 2

The second plot shows changes in pupil diameter during study as a function of serial position and one's WMC. Before plotting, we need to tidy the data a  bit more:

```{r fig2_prep}

#Reordering factor levels for legend
pupil_data$span_group <- factor(pupil_data$span_group, 
                                levels = c("Low", "Medium", "High"))

plot2data <- pupil_data %>%
  group_by(word, span_group) %>%
  summarise(mean_TEPR = mean(TEPR, na.rm = TRUE),
            se_TEPR = sundry::se(TEPR))

# Rename variable for legend
plot2data %<>% 
  rename("WMC" = `span_group`)

# Rename variables to enhance clarity
plot2data %<>% 
  mutate(WMC = recode(WMC, 
                             'Low' = "Low WMC",
                             'Medium' = "Medium WMC",
                             'High' = "High WMC"))

```

The following was my starting point (was Fig 5 in [Miller et al. 2019](https://www.sciencedirect.com/science/article/pii/S0749596X18300846)):

```{r fig2_showcodeonly, echo=TRUE, eval=FALSE}

plot2_OG <- plot2data %>%
  filter(WMC != "Medium WMC") %>%
  ggplot(aes(x = word, y = mean_TEPR)) +
  geom_line(aes(colour = WMC)) +
  geom_errorbar(aes(ymin = mean_TEPR - se_TEPR, 
                    ymax = mean_TEPR + se_TEPR,
                    color = WMC),
                    width = 0.4, 
                    size = 0.6) +
    scale_fill_grey() +
    # Add reference line for means of each group
    geom_line(aes(colour = WMC), size = 1) +
    scale_colour_grey() +
    theme_bw(base_size = 12) +
    # Change labels
    labs(caption = "Figure 2. Pupillary response across serial positions for low
                    working memory capacity (WMC) individuals (n = 31), medium 
                    WMC individuals (n = 69), and high WMC individuals (n = 33).",
           y = "Change in Pupil Diameter (mm)",
           x = "Serial position",
           colour = "WMC") +
   # Relabel x axis values to make more sense to reader
   scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
                      labels = c("1", "2", "3", "4", "5", 
                                 "6", "7", "8", "9", "10"),
                      limits = c(1, 10)) 
```

```{r fig2DNU, include=FALSE, echo=FALSE, eval=TRUE}
plot2_OG <- plot2data %>%
  filter(WMC != "Medium WMC") %>%
  ggplot(aes(x = word, y = mean_TEPR)) +
  geom_line(aes(colour = WMC)) +
  geom_errorbar(aes(ymin = mean_TEPR - se_TEPR, 
                    ymax = mean_TEPR + se_TEPR,
                    color = WMC),
                    width = 0.4, 
                    size = 0.6) +
    scale_fill_grey() +
    # Add reference line for means of each group
    geom_line(aes(colour = WMC), size = 1) +
    scale_colour_grey() +
    theme_bw(base_size = 12) +
    # Change labels
    labs(caption = "Figure 2. Pupillary response across serial positions for low working memory capacity 
(WMC) individuals (n = 31), medium WMC individuals (n = 69), and high WMC 
individuals (n = 33).",
           y = "Change in Pupil Diameter (mm)",
           x = "Serial position",
           colour = "WMC") +
   # Relabel x axis values to make more sense to reader
   scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
                      labels = c("1", "2", "3", "4", "5", 
                                 "6", "7", "8", "9", "10"),
                      limits = c(1, 10)) 
```

```{r fig2_print, fig.height=5, fig.width=6.5, fig.align='center'}
plot2_OG + academic_theme
```

Note that the legend is a bit confusing, as the order of WMC group doesn't quite map on to the ordering of the lines in the graph (e.g., high WMC is the uppermost line but is listed on the bottom of the legend). 

Again, the intended audience for this graph is the **scientific community**. The message to be communicated is that different patterns of pupil dilation across serial positions emerge based on one's working memory capacity (WMC). Namely, for high WMC individuals (*n* = 33), pupil diameter *increases* as each new word is introduced during the learning phase of the task. Alternatively, for low WMC individuals (*n* = 31), pupil diameter *decreases* as each new word is introduced during learning.

### Alternative Publication-Friendly Version of Plot 2

Next, I aim to improve the legend and map uncertainty via `geom_ribbon()`. I also want to include the full range of participants, so I will also plot the trend for medium WMC individuals:

```{r plot2v2USE, include=FALSE, echo=FALSE, eval=TRUE}
# Plot
plot2_academic <- ggplot(plot2data, aes(x = word, y = mean_TEPR)) +
    geom_ribbon(aes(ymin = mean_TEPR - se_TEPR, 
                    ymax = mean_TEPR + se_TEPR,
                    fill = WMC),
                    alpha = 0.8) +
    scale_fill_grey() +
    # Add reference line for means of each group
    geom_line(aes(colour = WMC), size = 1) +
    scale_colour_grey() +
    # Add labels for each WMC group
    geom_text(data = filter(plot2data, word == '10'),
            aes(y = mean_TEPR, label = WMC),
            color = "black",
            nudge_x = .20,
            hjust = 0,
            size = 4,
            family = "Times",
            fontface = 2) +
    theme_bw(base_size = 12) +
    # Left-align caption
    theme(legend.position = "none") +
    # Change labels
    labs(caption = "Figure 2. Pupillary response across serial positions for low working memory capacity 
(WMC) individuals (n = 31), medium WMC individuals (n = 69), and high WMC 
individuals (n = 33).",
           y = "Change in Pupil Diameter (mm)",
           x = "Serial position",
           colour = "") +
   # Relabel x axis values to make more sense to reader
   scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
                      labels = c("1", "2", "3", "4", "5", 
                                 "6", "7", "8", "9", "10"),
                      limits = c(1, 12)) 
```

```{r plot2v2_showcodeonly, echo=TRUE, eval=FALSE}
# Plot
plot2_academic <- ggplot(plot2data, aes(x = word, y = mean_TEPR)) +
    geom_ribbon(aes(ymin = mean_TEPR - se_TEPR, 
                    ymax = mean_TEPR + se_TEPR,
                    fill = WMC),
                    alpha = 0.8) +
    scale_fill_grey() +
    # Add reference line for means of each group
    geom_line(aes(colour = WMC), size = 1) +
    scale_colour_grey() +
    # Add labels for each WMC group
    geom_text(data = filter(plot2data, word == '10'),
            aes(y = mean_TEPR, label = WMC),
            color = "black",
            nudge_x = .20,
            hjust = 0,
            size = 4,
            family = "Times",
            fontface = 2) +
    theme_bw(base_size = 12) +
    # Left-align caption
    theme(legend.position = "none") +
    # Change labels
    labs(caption = "Figure 2. Pupillary response across serial positions for low 
                    working memory capacity (WMC) individuals (n = 31), medium 
                    WMC individuals (n = 69), and high WMC individuals (n = 33).",
           y = "Change in Pupil Diameter (mm)",
           x = "Serial position",
           colour = "") +
   # Relabel x axis values to make more sense to reader
   scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
                      labels = c("1", "2", "3", "4", "5", 
                                 "6", "7", "8", "9", "10"),
                      limits = c(1, 12)) 
```

```{r tidy_data_plot2USE, fig.height=5, fig.width=6.5, fig.align='center'}
plot2_academic + academic_theme
```

### Fancier/Prettier Version of Plot 2

Now I add some color and apply my own personal theme:

```{r plot2_funDNU, include=FALSE, echo=FALSE, eval=TRUE}
#Specify colors for my own color palette
outrun <- c("violetred4", "pink", "turquoise4")

#Plot
plot2_fun <- ggplot(plot2data, aes(x = word, y = mean_TEPR)) +
    geom_ribbon(aes(ymin = mean_TEPR - se_TEPR, 
                    ymax = mean_TEPR + se_TEPR,
                    fill = WMC),
                    alpha = 0.4) +
    scale_fill_manual(values =  outrun) +
    geom_line(aes(colour = WMC), size = 1) +
    scale_colour_manual(values = outrun) +
    # Add labels for each WMC group
    geom_text(data = filter(plot2data, word == '10'),
            aes(y = mean_TEPR, label = WMC),
            color = "gray80",
            nudge_x = .20,
            hjust = 0,
            size = 4,
            fontface = 2) +
    theme_minimal(base_size = 12) +
    # Left-align caption
    theme(legend.position = "none") +
    # Change labels
    labs(caption = "Figure 2. Pupillary response across serial positions for low working memory capacity 
(WMC) individuals (n = 31), medium WMC individuals (n = 69), and high WMC 
individuals (n = 33).",
           y = "Change in Pupil Diameter (mm)",
           x = "Serial position",
           colour = "") +
   # Relabel x axis values to make more sense to reader
   scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
                      labels = c("1", "2", "3", "4", "5", 
                                 "6", "7", "8", "9", "10"),
                      limits = c(1, 12)) 
```

```{r p2funv3_print, fig.height=5, fig.width=6.5, fig.align='center'}
plot2_fun + bbg_darktheme
```

MUCH improved--Am I right?!

## Plot 3

The third plot shows changes in pupil diameter as a function of serial position [broken down into Primacy (words 1–3), Mid (words 4–7), and Recency (words 8–10)] and bin, the time across the 3 second study phase for each word, based on one's WMC. Of course, to plot this, we need to tidy the data even more:

```{r fig3_tidy}
# Converting word # to factors
pupil_data$word <- as.factor(pupil_data$word)

# Breaking down words into primacy, mid, and recency items
plot3_data <- pupil_data %>% 
  mutate(word = recode(word, '1' = "Primacy Items",
                             '2' = "Primacy Items",
                             '3' = "Primacy Items",
                             '4' = "Mid Items",
                             '5' = "Mid Items", 
                             '6' = "Mid Items",
                             '7' = "Mid Items",
                             '8' = "Recency Items",
                             '9' = "Recency Items",
                            '10' = "Recency Items"))

plot3_data %<>%
  group_by(word, bin, span_group) %>%
  summarise(mean_TEPR = mean(TEPR, na.rm = TRUE),
            se_TEPR = sundry::se(TEPR))

# Specify factor levels
plot3_data$word <- factor(plot3_data$word, 
                                levels = c("Primacy Items", 
                                           "Mid Items", 
                                           "Recency Items"))

# Rename variables to enhance clarity
plot3_data %<>% 
  mutate(span_group = recode(span_group, 
                             'Low' = "Low WMC",
                             'Medium' = "Medium WMC",
                             'High' = "High WMC"))
```

Below is the plot 3's starting point (was Fig 6. in [Miller et al. 2019](https://www.sciencedirect.com/science/article/pii/S0749596X18300846)). Note that error bars aren't even provided!:

```{r plot3OG_DNU, include=FALSE, echo=FALSE, eval=TRUE}
plot3_OG <- plot3_data %>%
  filter(span_group != "Medium WMC") %>%
  ggplot(aes(x = bin, y = mean_TEPR, colour = word)) +
    geom_line(aes(linetype = word), size = 1.3) +
    scale_linetype_manual(values=c("dotted", "twodash", "solid"),
                          name  ="Serial Position",
                          breaks=c("Primacy Items", "Mid Items", "Recency Items"),
                          labels=c("Primacy", "Mid", "Recency")) +
    scale_colour_manual(values = c("gray0", "gray50", "gray75"),
                          name  ="Serial Position",
                          breaks=c("Primacy Items", "Mid Items", "Recency Items"),
                          labels=c("Primacy", "Mid", "Recency")) +
    facet_wrap(~span_group) +
    theme_bw(base_size = 14) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          plot.subtitle = element_text(face = "bold", hjust = 0.5),
          strip.text = element_text(size = 11),
          legend.position = "bottom") +
        # Change labels
        labs(caption = "Figure 3. Pupil diameter as a function of serial position and time across encoding period for low WMC (n = 31), medium WMC 
(n = 69), and high WMC (n = 33) individuals. Serial position was broken down into Primacy (words 
1–3), Mid (words 4–7), and Recency (words 8–10) for graphical purposes only.",
             y = "Changes in Pupil Diameter (mm)",
             x = "Time (ms)") +
        # Adjust/Relabel x axis values to make more sense to reader
        scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14),
                           labels = c("0", "400", "800", "1,200", 
                                      "1,600", "2,000", "2,400","2,800"),
                           limits = c(0, NA)) +
        # Adjust/Relabel y axis values to make more sense to reader
        scale_y_continuous(breaks = c(-0.10, -0.05, 0.00, 0.05, 0.10, 0.15),
                           label = c("-0.10", "-0.05", "0.00", 
                                     "0.05", "0.10", "0.15"),
                           limits = c(-0.10, 0.15))
```

```{r plot3OG_showcodeonly, echo=TRUE, eval=FALSE}
plot3_OG <- plot3_data %>%
  filter(span_group != "Medium WMC") %>%
  ggplot(aes(x = bin, y = mean_TEPR, colour = word)) +
    geom_line(aes(linetype = word), size = 1.5) +
    scale_linetype_manual(values=c("dotted", "twodash", "solid"),
                          name  ="Serial Position",
                          breaks=c("Primacy Items", "Mid Items", "Recency Items"),
                          labels=c("Primacy", "Mid", "Recency")) +
    scale_colour_manual(values = c("gray0", "gray50", "gray75"),
                          name  ="Serial Position",
                          breaks=c("Primacy Items", "Mid Items", "Recency Items"),
                          labels=c("Primacy", "Mid", "Recency")) +
    facet_wrap(~span_group) +
    theme_bw(base_size = 14) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          plot.subtitle = element_text(face = "bold", hjust = 0.5),
          strip.text = element_text(size = 11),
          legend.position = "bottom") +
        # Change labels
        labs(caption = "Figure 3. Pupil diameter as a function of serial position
                        and time across encoding period for low WMC (n = 31), 
                        medium WMC (n = 69), and high WMC (n = 33) individuals. 
                        Serial position was broken down into Primacy (words 1–3), 
                        Mid (words 4–7), and Recency (words 8–10) for graphical 
                        purposes only.",
             y = "Changes in Pupil Diameter (mm)",
             x = "Time (ms)") +
        # Adjust/Relabel x axis values to make more sense to reader
        scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14),
                           labels = c("0", "400", "800", "1,200", 
                                      "1,600", "2,000", "2,400","2,800"),
                           limits = c(0, NA)) +
        # Adjust/Relabel y axis values to make more sense to reader
        scale_y_continuous(breaks = c(-0.10, -0.05, 0.00, 0.05, 0.10, 0.15),
                           label = c("-0.10", "-0.05", "0.00", 
                                     "0.05", "0.10", "0.15"),
                           limits = c(-0.10, 0.15))
```

```{r fig.align='center'}
plot3_OG + academic_theme
```

The intended audience is yet again the **scientific community**, and the plot essentially conveys the same information as the plot above (plot #2). That is, when instructed to study a list of words for a later test, two factors seem to influence how attention is allocated across the study phase for each word (as indexed via pupil dilation): (1) one's WMC and (2) serial position. For high WMC individuals, pupil dilation continues to gradually increase throughout the encoding period for all serial positions, with primacy items (the first few words presented during list presentation; words 1-3) displaying smaller dilations than mid (words 4–7) and recency items (the last few words presented during list presentation; words 8–10). Conversely, low WMC individuals show moderate increases in dilation that appear to plateau near the middle of the encoding period. Moreover, pupil dilation appears to be largest for primacy items and smallest for recency items, despite a gradual increase in dilation for recency items.

### Alternative Publication-Friendly Version of Plot 3

Here I re-create this plot but map uncertainty/standard errors via `geom_smooth()`:

```{r plot3_academicDNU, echo=FALSE, eval=TRUE, include = FALSE}
plot3_academic <- ggplot(plot3_data, aes(x = bin, y = mean_TEPR, colour = word)) +
    geom_smooth(aes(linetype = word)) +
    scale_linetype_manual(values=c("dotted", "twodash", "solid"),
                          name  ="Serial Position",
                          breaks=c("Primacy Items", "Mid Items", "Recency Items"),
                          labels=c("Primacy", "Mid", "Recency")) +
    scale_colour_manual(values = c("gray0", "gray50", "gray75"),
                          name  ="Serial Position",
                          breaks=c("Primacy Items", "Mid Items", "Recency Items"),
                          labels=c("Primacy", "Mid", "Recency")) +
    facet_wrap(~span_group) +
    theme_bw(base_size = 12) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          plot.subtitle = element_text(face = "bold", hjust = 0.5),
          strip.text = element_text(size = 11),
          legend.position = "bottom") +
        # Change labels
        labs(caption = "Figure 3. Pupil diameter as a function of serial position and time across encoding period for low WMC (n = 31), medium WMC 
(n = 69), and high WMC (n = 33) individuals. Serial position was broken down into Primacy (words 
1–3), Mid (words 4–7), and Recency (words 8–10) for graphical purposes only.",
             y = "Changes in Pupil Diameter (mm)",
             x = "Time (ms)") +
        # Adjust/Relabel x axis values to make more sense to reader
        scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14),
                           labels = c("0", "400", "800", "1,200", 
                                      "1,600", "2,000", "2,400","2,800"),
                           limits = c(0, NA)) +
        # Adjust/Relabel y axis values to make more sense to reader
        scale_y_continuous(breaks = c(-0.10, -0.05, 0.00, 0.05, 0.10, 0.15),
                           label = c("-0.10", "-0.05", "0.00", 
                                     "0.05", "0.10", "0.15"),
                           limits = c(-0.10, 0.15))
```

```{r p3academv2_showcodeonly, eval=FALSE, echo=TRUE}
plot3_academic <- ggplot(plot3_data, aes(x = bin, y = mean_TEPR, colour = word)) +
    geom_smooth(aes(linetype = word)) +
    scale_linetype_manual(values=c("dotted", "twodash", "solid"),
                          name  ="Serial Position",
                          breaks=c("Primacy Items", "Mid Items", "Recency Items"),
                          labels=c("Primacy", "Mid", "Recency")) +
    scale_colour_manual(values = c("gray0", "gray50", "gray75"),
                          name  ="Serial Position",
                          breaks=c("Primacy Items", "Mid Items", "Recency Items"),
                          labels=c("Primacy", "Mid", "Recency")) +
    facet_wrap(~span_group) +
    theme_bw(base_size = 12) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          plot.subtitle = element_text(face = "bold", hjust = 0.5),
          strip.text = element_text(size = 11),
          legend.position = "bottom") +
        # Change labels
        labs(caption = "Figure 3. Pupil diameter as a function of serial position
                        and time across encoding period for low WMC (n = 31), 
                        medium WMC (n = 69), and high WMC (n = 33) individuals. 
                        Serial position was broken down into Primacy (words 1–3), 
                        Mid (words 4–7), and Recency (words 8–10) for graphical 
                        purposes only.",
             y = "Changes in Pupil Diameter (mm)",
             x = "Time (ms)") +
        # Adjust/Relabel x axis values to make more sense to reader
        scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14),
                           labels = c("0", "400", "800", "1,200", 
                                      "1,600", "2,000", "2,400","2,800"),
                           limits = c(0, NA)) +
        # Adjust/Relabel y axis values to make more sense to reader
        scale_y_continuous(breaks = c(-0.10, -0.05, 0.00, 0.05, 0.10, 0.15),
                           label = c("-0.10", "-0.05", "0.00", 
                                     "0.05", "0.10", "0.15"),
                           limits = c(-0.10, 0.15))
```

```{r p3academv2_print, fig.align='center'}
plot3_academic + academic_theme
```

### Fancier/Prettier Version of Plot 3

This time, not only am I going to apply my own theme, but I will map uncertainty with a hypothetical outcome plot (HOP). Basically, like plot 1, uncertainty is mapped via generation of outcome draws from a fitted model. HOPS just animate this process so that the audience can observe changes across hypothetical samples.

```{r plot3_funDNU, include=FALSE, eval=TRUE, echo=FALSE}

plot3_fun <- ggplot(plot3_data, aes(x = bin, y = mean_TEPR, colour = word)) +
      # Generate outcome draws from a fitted model
      stat_smooth_draws(times = 10,
                        aes(group = interaction(stat(.draw), colour)),
                        size = 0.8) +
      scale_color_manual(values = outrun) +
      #scale_color_carto_d(palette = "Burg") +
      # Create seperate plots for people with low, mid, and high WMC
      facet_wrap(~span_group) +
      # Specifying sampled draws in addition to the animated lines
      transition_states(stat(.draw), 1, 2) +
      enter_fade() + exit_fade() +
      shadow_mark(future = TRUE, size = 0.25, color = "gray50", alpha = 1/4) +
      theme_minimal(base_size = 12) +
      # Rotate x axis values so they are angled; center subtitle
      # Left-align caption
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            plot.subtitle = element_text(face = "bold", hjust = 0.5),
            strip.text = element_text(size = 11),
            legend.position = "bottom") +
      # Change labels
      labs(caption = "Figure 3. Pupil diameter as a function of serial position and time across encoding period for low WMC 
(n = 31), medium WMC (n = 69), and high WMC (n = 33) individuals. Serial position was broken down 
into Primacy (words 1–3), Mid (words 4–7), and Recency (words 8–10) for graphical purposes only.",
           y = "Mean Pupil Diameter (mm)",
           x = "Time (ms)",
           colour = "Serial Position") +
      # Adjust/Relabel x axis values to make more sense to reader
      scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14),
                         labels = c("0", "400", "800", "1,200", 
                                    "1,600", "2,000", "2,400","2,800"),
                         limits = c(0, NA)) +
      # Adjust/Relabel y axis values to make more sense to reader
      scale_y_continuous(breaks = c(-0.10, -0.05, 0.00, 0.05, 0.10, 0.15),
                         label = c("-0.10", "-0.05", "0.00", 
                                   "0.05", "0.10", "0.15"),
                         limits = c(-0.10, 0.15))
```

```{r plot3fun_showcodeonly, eval=FALSE, echo=TRUE}

plot3_fun <- ggplot(plot3_data, aes(x = bin, y = mean_TEPR, colour = word)) +
      # Generate outcome draws from a fitted model
      stat_smooth_draws(times = 10,
                        aes(group = interaction(stat(.draw), colour)),
                        size = 0.8) +
      # Specify colors I want
      scale_color_manual(values = outrun) +
      # Create seperate plots for people with low, mid, and high WMC
      facet_wrap(~span_group) +
      # Specifying sampled draws in addition to the animated lines
      transition_states(stat(.draw), 1, 2) +
      enter_fade() + exit_fade() +
      shadow_mark(future = TRUE, size = 0.25, color = "gray50", alpha = 1/4) +
      theme_minimal(base_size = 14) +
      # Rotate x axis values so they are angled; center subtitle
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            plot.subtitle = element_text(face = "bold", hjust = 0.5),
            strip.text = element_text(size = 14),
            legend.position = "bottom")) +
      # Change labels
      labs(caption = "Figure 3. Pupil diameter as a function of serial position 
                      and time across encoding period for low WMC (n = 31), 
                      medium WMC (n = 69), and high WMC (n = 33) individuals. 
                      Serial position was broken down into Primacy (words 1–3), 
                      Mid (words 4–7), and Recency (words 8–10) for graphical 
                      purposes only.",
           y = "Mean Pupil Diameter (mm)",
           x = "Time (ms)",
           colour = "Serial Position") +
      # Adjust/Relabel x axis values to make more sense to reader
      scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14),
                         labels = c("0", "400", "800", "1,200", 
                                    "1,600", "2,000", "2,400","2,800"),
                         limits = c(0, NA)) +
      # Adjust/Relabel y axis values to make more sense to reader
      scale_y_continuous(breaks = c(-0.10, -0.05, 0.00, 0.05, 0.10, 0.15),
                         label = c("-0.10", "-0.05", "0.00", 
                                   "0.05", "0.10", "0.15"),
                         limits = c(-0.10, 0.15))
```

```{r plot3_fun_print, fig.align='center'}
plot3_fun + bbg_darktheme
```

## BONUS Plot 4

This final plot is meant to be more digestible for the **general public**; it doesn't examine pupillometry data. Rather, the plot shows the relation between recall accuracy and strategy type. The intended message to be communicated is that strategies that rely on more elaborative mental processes are associated with better memory performance.

Here I prep the data and create a standard, but fancy-ish, bar-plot:

```{r plot4DNU, include=FALSE, eval=TRUE, echo=FALSE}

# Select variables of interest
strategy_data <- data %>%
  select(-sp1_acc:-sp10_acc,
         -ospan:-span_group,
         -primacy_recall:-ebin15w10pt4_mean) %>%
  gather(key = strat_type, value = response, passive_read_strat:other_strat)

#levels(as.factor(strategy_data$strat_type))

# Filter out NAs, convert strategy type and score to factors, and recode strat
strategy_data %<>%
  filter(response != "NA") %>%
  mutate(strat_type = as.factor(strat_type),
         response = as.factor(response),
         strat_type = recode(strat_type,
                             "grouping_strat" = "Grouping",
                             "imagery_strat" = "Imagery",
                             "other_strat" = "Other",
                             "passive_read_strat" = "Passive Reading",
                             "rehearsal_strat" = "Rote Rehearsal",
                             "sentence_gen_strat" = "Sentence Generation")) 

# Obtain summary stats
strategy_data %<>%
  group_by(strat_type, response) %>%
  summarise(mean_acc = mean(accuracy_mean, na.rm = TRUE),
            se_acc = sundry::se(accuracy_mean))

# Specify factor levels
# Effective strategies = imagery, sentence generation, and grouping
# Ineffective strategies = rehearsal and passive reading
strategy_data$strat_type <- factor(strategy_data$strat_type, 
                                levels = c("Imagery", 
                                           "Sentence Generation", 
                                           "Grouping",
                                           "Rote Rehearsal", 
                                           "Passive Reading", 
                                           "Other"))

plot4 <- strategy_data %>%
  #filter out other and grouping strategy
  filter(strat_type != "Other" & strat_type != "Grouping") %>%
  ggplot(aes(response, mean_acc, fill = response)) +
      geom_col(width = 0.60, 
               alpha = 0.6) +
      geom_errorbar(aes(ymin = mean_acc + qnorm(0.025)*se_acc, 
                          ymax = mean_acc + qnorm(0.975)*se_acc),
                          color = "gray40",
                          width = 0.4, 
                          size = 0.8) +
      # Print accuracy associated with each condition
      geom_text(aes(response, mean_acc, label = paste0(round(mean_acc*100), "%")),
                nudge_y = 0.15, # Specifies how high above bar text appears
                size = 3,
                color = "gray80") +
      # Provide seperate graphs for each strategy
      facet_wrap(~strat_type) +
      scale_fill_carto_d(palette = "Burg") +
      theme_minimal() +
      # Delete legend, left-align caption, center title
      theme(legend.position="none",
            plot.caption = element_text(hjust = 0),
            strip.text = element_text(size = 11),
            plot.title = element_text(hjust = 0.5)) +
      #Modify labels
      labs(title = "Recall Accuracy as a Function of Strategy Type and Use of Strategy",
               y = "Mean Recall Accuracy",
               x = "",
               caption = "'No' represents individuals who did not report using given strategy, whereas 'Yes' represents those who used 
said strategy. Note that performance is actually better among people who report not using a normatively 
ineffective strategy (e.g., rote rehearsal or passive reading) than when people report using these strategies.") +
      # Rename labels on x-axis
      scale_x_discrete(breaks = c(0, 1),
                       labels = c("No", "Yes")) +
      # Modify names/range of y-axis 
      scale_y_continuous(breaks = c(0, 0.2, 0.4, 0.6, 0.8),
                         labels = c("0%", "20%", "40%", "60%", "80%"),
                         limits = c(0, 0.8))
```

```{r plot4_showcodeonly, eval=FALSE, echo=TRUE}
# Select variables of interest
strategy_data <- data %>%
  select(-sp1_acc:-sp10_acc,
         -ospan:-span_group,
         -primacy_recall:-ebin15w10pt4_mean) %>%
  gather(key = strat_type, value = response, passive_read_strat:other_strat)

# Filter out NAs, convert strategy type and score to factors, and recode strat
strategy_data %<>%
  filter(response != "NA") %>%
  mutate(strat_type = as.factor(strat_type),
         response = as.factor(response),
         strat_type = recode(strat_type,
                             "grouping_strat" = "Grouping",
                             "imagery_strat" = "Imagery",
                             "other_strat" = "Other",
                             "passive_read_strat" = "Passive Reading",
                             "rehearsal_strat" = "Rote Rehearsal",
                             "sentence_gen_strat" = "Sentence Generation")) 

# Obtain summary stats
strategy_data %<>%
  group_by(strat_type, response) %>%
  summarise(mean_acc = mean(accuracy_mean, na.rm = TRUE),
            se_acc = sundry::se(accuracy_mean))

# Specify factor levels
# Effective strategies = imagery, sentence generation, and grouping
# Ineffective strategies = rehearsal and passive reading
strategy_data$strat_type <- factor(strategy_data$strat_type, 
                                levels = c("Imagery", 
                                           "Sentence Generation", 
                                           "Grouping",
                                           "Rote Rehearsal", 
                                           "Passive Reading", 
                                           "Other"))

plot4 <- strategy_data %>%
  #filter out other and grouping strategy
  filter(strat_type != "Other" & strat_type != "Grouping") %>%
  ggplot(aes(response, mean_acc, fill = response)) +
      geom_col(width = 0.60, 
               alpha = 0.6) +
      geom_errorbar(aes(ymin = mean_acc + qnorm(0.025)*se_acc, 
                          ymax = mean_acc + qnorm(0.975)*se_acc),
                          color = "gray40",
                          width = 0.4, 
                          size = 0.8) +
      # Print accuracy associated with each condition
      geom_text(aes(response, mean_acc, label = paste0(round(mean_acc*100), "%")),
                nudge_y = 0.15, # Specifies how high above bar text appears
                size = 3,
                color = "gray80") +
      # Provide seperate graphs for each strategy
      facet_wrap(~strat_type) +
      # Specify color palette
      scale_fill_carto_d(palette = "Burg") +
      theme_minimal() +
      # Delete legend, left-align caption, center title
      theme(legend.position="none",
            plot.caption = element_text(hjust = 0),
            strip.text = element_text(size = 12),
            plot.title = element_text(hjust = 0.5)) +
      #Modify labels
      labs(title = "Recall Accuracy as a Function of Strategy Type and Use of Strategy",
               y = "Mean Recall Accuracy",
               x = "",
               caption = "'No' represents individuals who did not report using 
                          given strategy, whereas 'Yes' represents those who used 
                          said strategy. Note that performance is actually better 
                          among people who report not using a normatively 
                          ineffective strategy (e.g., rote rehearsal or passive 
                          reading) than when people report using these strategies.") +
      # Rename labels on x-axis
      scale_x_discrete(breaks = c(0, 1),
                       labels = c("No", "Yes")) +
      # Modify names/range of y-axis 
      scale_y_continuous(breaks = c(0, 0.2, 0.4, 0.6, 0.8),
                         labels = c("0%", "20%", "40%", "60%", "80%"),
                         limits = c(0, 0.8))
```

```{r plot4_print, fig.height = 5, fig.width = 8, fig.align='center'}
# Applying my theme to plot
plot4 + bbg_darktheme
```

One problem with the above plot, however, is that a general audience may not understand what the error bars represent. So, instead, I'm going to map uncertainty with `density stripes`. Again, I recommend checking out the [ungeviz](https://wilkelab.org/ungeviz/index.html) package for more details. 

```{r plot4v2DNU, echo=FALSE, include=FALSE, eval=TRUE}
#Specify colors I want to use for density stripes 
stripe_colors <- c("#7F38A7", "#42B9BD")
#Specify colors I want to use for cooresponding mean stripe
bar_colors <- c("#5F2A7C", "#31898C")

plot4v2 <- strategy_data %>%
  #filter out other and grouping strategy
  filter(strat_type != "Other" & strat_type != "Grouping") %>%
    ggplot(aes(mean_acc, response, group = response, fill = response)) +
        # Add density stripes to mark region of standard error
        stat_confidence_density(aes(moe = se_acc),
                                height = 0.5) +
        scale_fill_manual(values = stripe_colors) +
        # Add vertical line where mean is for each condition
        geom_vpline(aes(colour = response),
                    stat = "summary",
                    size = 0.9) +
        scale_colour_manual(values = bar_colors) +
        # Create seperate sections based on strategy type
        facet_wrap(~strat_type, nrow = 1) +
        # Print accuracy associated with each condition
        geom_text(aes(mean_acc, response, label = paste0(round(mean_acc*100), "%")),
                  nudge_x = 0.005,
                  nudge_y = 0.3,
                  size = 3,
                  color = "gray80") +
        theme_minimal() +
        # Delete legend, increase size of facet labels, and center title
        theme(legend.position = "none",
              strip.text = element_text(size = 11),
              plot.title = element_text(hjust = 0.5)) +
        labs(title = "Recall Accuracy as a Function of Strategy Type and Use of Strategy",
                     y = "",
                     x = "Mean Recall Accuracy",
                     caption = "'No' represents individuals who did not report using given strategy, whereas 'Yes' represents those who used 
said strategy. Note that performance is actually better among people who report not using a normatively 
ineffective strategy (e.g., rote rehearsal or passive reading) than when people report using these strategies.") +
        # Rename labels on x-axis
        scale_y_discrete(breaks = c(0, 1),
                         labels = c("No", "Yes")) +
        # Modify names/range of y-axis 
        scale_x_continuous(breaks = c(0.45, 0.50, 0.55, 0.6, 0.65, 0.70),
                           labels = c("0.45%", "", "55%" , "", "65%", ""),
                           limits = c(0.40, 0.70))
```

```{r plot4v2_showcodeonly, eval=FALSE, echo=TRUE}
#Specify colors I want to use for density stripes 
stripe_colors <- c("#7F38A7", "#42B9BD")
#Specify colors I want to use for cooresponding mean stripe
bar_colors <- c("#5F2A7C", "#31898C")

plot4v2 <- strategy_data %>%
  #filter out other and grouping strategy
  filter(strat_type != "Other" & strat_type != "Grouping") %>%
    ggplot(aes(mean_acc, response, group = response, fill = response)) +
        # Add density stripes to mark region of standard error
        stat_confidence_density(aes(moe = se_acc),
                                height = 0.5) +
        scale_fill_manual(values = stripe_colors) +
        # Add vertical line where mean is for each condition
        geom_vpline(aes(colour = response),
                    stat = "summary",
                    size = 0.9) +
        scale_colour_manual(values = bar_colors) +
        # Create seperate sections based on strategy type
        facet_wrap(~strat_type, nrow = 1) +
        # Print accuracy associated with each condition
        geom_text(aes(mean_acc, response, 
                      label = paste0(round(mean_acc*100), "%")),
                  nudge_x = 0.005,
                  nudge_y = 0.3,
                  size = 3,
                  color = "gray80") +
        theme_minimal() +
        # Delete legend, increase size of facet labels, and center title
        theme(legend.position = "none",
              strip.text = element_text(size = 11),
              plot.title = element_text(hjust = 0.5)) +
        labs(title = "Recall Accuracy as a Function of Strategy Type and Use of Strategy",
             y = "",
             x = "Mean Recall Accuracy",
             caption = "'No' represents individuals who did not report using given 
                       strategy, whereas 'Yes' represents those who used said strategy. 
                       Note that performance is actually better among people who report 
                       not using a normatively ineffective strategy (e.g., rote 
                       rehearsal or passive reading) than when people report using 
                       these strategies.") +
        # Rename labels on x-axis
        scale_y_discrete(breaks = c(0, 1),
                         labels = c("No", "Yes")) +
        # Modify names/range of y-axis 
        scale_x_continuous(breaks = c(0.45, 0.50, 0.55, 0.6, 0.65, 0.70),
                           labels = c("0.45%", "", "55%" , "", "65%", ""),
                           limits = c(0.40, 0.70))
```

```{r plot4v2_print, fig.height = 5, fig.width = 8, fig.align='center'}
plot4v2 + bbg_darktheme
```

Personally, I think this looks pretty cool.

## Wrap Up

To review, rather than using traditional error bars to map uncertainty, `R` provides us with many alternatives, such as bootstrapping/generation of outcome draws from a fitted model, `geom_ribbon()`, `geom_smooth()`, HOPS, and density stripes. It is my hope to learn how to also create an interactive plot.. stay tuned.

Thanks for the read! :)
